---
title: "ELT Study"
runtime: shiny
#output: html_document
output: 
    flexdashboard::flex_dashboard:
           vertical_layout: scroll
           orientation: rows
---

```{r, echo = FALSE}
library(flexdashboard)
library(highcharter)
library(ggplot2)
library(devtools)
library(plotly)
library(shiny)
library(DT) ## tem que vir depois do shiny
library(dplyr)
library(readr)
library(pander)
#path <<- renderText({input$file1$datapath})
```

Page 1 {data-orientation=rows}
=====================================

Row {data-height=100}
-------------------------------------

```{r}
 fileInput('file1', 'Choose CSV File',
   accept=c('text/csv',
     'text/comma-separated-values,text/plain',
     '.csv'))

#plotOutput("eltp", height = "100%")


elt <- reactive({
    inFile <- input$file1
    if (is.null(inFile)) return(NULL)
   data <- read.csv(inFile$datapath)
   data
})  
```


Row 
-------------------------------------

### ELT

 All the information needed to generate the EP curves is stored in the ELT.
We will assume that this ELT corresponds to the Ground Up financial perspective. According to this ELT, a Northern San Andreas 6.5 earthquake has an annual rate of occurrence of 0.01. This earthquake happens on average once every 100 years. An exposure amount of 5.5 million is susceptible to this event. 

 In addition, we can expect, on average, ground up losses of 1.5 million from that 5.5 million of exposure if this event occurs. However, we must recognize the fact that the loss amount may be greater than or less than the 1.5 million expected loss value since the standard deviation is greater than zero. This will prove to be a key issue when generating the severity distribution.


```{r message=FALSE, echo=FALSE, comment = NA }
DT::renderDataTable({
   validate(
      need(!is.null(elt()), "Please select a data set")
    ) 
  DT::datatable(elt(), 
                options = list(pageLength = 5,
    initComplete = JS(
    "function(settings, json) {",
    "$(this.api().table().header()).css({'background-color': '#000', 'color': '#fff'});",
    "}")
    )
  ) %>% formatCurrency(3:5," " , mark = " ",digits = 0)
})

 
#reactive({ 
  
#dataTableOutput("table")
```

Page 2 {data-orientation=Row}
=====================================

Row {data-height=400}
-------------------------------------

### Exposure vesus Expected Loss
Shows loss expected if a particular event occurs.

###

```{r}
#highchartOutput("hcontainer",height = "500px")
  renderHighchart({
  validate(
      need(elt() != "", "Please select a data set")
    )   
#    validate(need(elt(),"Dataframe not found"))
hc <- highchart() %>% 
  hc_xAxis(categories = elt()$Exposure,
           labels=list(format="{value:,.0f}")) %>%   
  hc_add_series(name = "ExpectedLoss",
                data = elt()$ExpectedLoss) 
hc <- hc %>% 
  hc_chart(type = "column",
           options3d = list(enabled = TRUE, beta = 15, alpha = 15))
hc %>% 
  hc_chart(borderColor = '#EBBA95',
           borderRadius = 10,
           borderWidth = 2,
           backgroundColor = list(
             linearGradient = c(0, 0, 500, 500),
             stops = list(
               list(0, 'rgb(255, 255, 255)'),
               list(1, 'rgb(200, 200, 255)')
             )))
})
```

Row {data-height=400}
-------------------------------------

### OEP curve
 The Occurrence exceedance probability (OEP) curve shows the probability that the losses for at least one occurrence will exceed a threshold.

 Since the OEP curve is the cumulative distribution for the largest occurrence in a year, it can be used to analyze occurrence-based situations. For example, we can calculate the probability of activating and exhausting occurrence-based contracts such as a policy or reinsurance treaty from OEP curves. In addition, the OEP curve can provide statistical information on single event covers.



```{r message=FALSE, echo=FALSE, comment = NA}
oepf <- 
  reactive({
#  if (is.null(elt())) return(NULL)
  validate(
      need(elt() != "", "Please select a data set")
    )  
  l <- sum(elt()$Rate)
  thresholds <- seq(0,max(elt()$ExpectedLoss),max(elt()$ExpectedLoss)/4)
  thresholds <- as.data.frame(thresholds)
  
  eltc <- elt() %>% mutate(mu    = ExpectedLoss / Exposure, 
                         sigma = SD/Exposure,
                         alpha = ((1 - mu) / sigma^2 - 1 / mu) * mu ^ 2,
                         beta  =  alpha * (1 / mu - 1)
  )
  
   pr <- as.numeric()
  cep <- as.numeric()
  oep <- as.numeric()
  
  for(i in 1:nrow(thresholds)){
    for(j in 1:nrow(eltc)){
      pr[j]  <- 1 - pbeta(thresholds[i,]/eltc$Exposure[j], eltc$alpha[j], eltc$beta[j]) 
    }
    cep[i] <- sum(eltc$Rate * pr) / sum(eltc$Rate) 
    oep[i] <- 1 - exp(-l*cep[i])
  }
  oepdf <- data.frame(thresholds=thresholds[,1],cep,oep)
  
  return(oepdf)
  })
```

###

```{r results='asis', message=FALSE, echo=FALSE, comment = NA}
renderHighchart({
#validate(need(oepf(),"Dataframe not found"))
validate(
      need(oepf() != "", "Please select a data set")
    )   
hc <- highchart() %>% hc_title(text = "OEP") %>%
  hc_subtitle(text = "Occurrence exceedance probability") %>% 
  hc_xAxis(categories = oepf()$thresholds,
           labels=list(format="{value:,.0f}")) %>%  #numeros maiores que 1000 separados 
  hc_add_series(name = "oep", 
                data = oepf()$oep*100) %>%
  hc_yAxis(#title = list(text = "percentage of tastiness"),
           labels = list(format = "{value}%"), max =10) %>%   
  hc_tooltip(formatter = JS("function(){
              return ('Thresholds:  ' + Highcharts.numberFormat(this.x, 0, '.', ' ')  + ' <br> OEP: ' + Highcharts.numberFormat(this.y,2) + '%' )}"))
    
              #valueDecimals= 2,
             #valuePrefix: '$',
              # valueSuffix= '%'
            
hc %>% 
  hc_chart(borderColor = '#EBBA95',
           borderRadius = 10,
           borderWidth = 2,
           backgroundColor = list(
             linearGradient = c(0, 0, 500, 500),
             stops = list(
               list(0, 'rgb(255, 255, 255)'),
               list(1, 'rgb(200, 200, 255)')
             ))) 
 })


```   


